---
title: "Analyses"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  message = FALSE,
  warning = TRUE,
  cache = FALSE,
  autodep = TRUE
  )

```



# Load dependencies

Source `dependencies.R`.

```{r dependencies, message=FALSE, cache=FALSE, code=readr::read_lines(here::here("code/_dependencies.R"))}
source(here::here("code/_dependencies.R"))

```






# Experiment 1

## Load data

```{r load_data_experiment1}
tbl_participants_1 <- read_rds(here("output/study1/tbl_participants.rds"))
tbl_targeting_1 <- read_rds(here("output/study1/tbl_targeting.rds"))

```


## Augment data

```{r tbl_targeting_performance_1}
tbl_targeting_performance_1 <- tbl_targeting_1 %>%
  group_by_at(vars(
    id,
    condition,
    contains("extr"),
    contains("ATI")
  )) %>%
  summarize(acc = mean(dec_correct),
            conf_in_correct = mean(conf_in_correct)) %>%
  ungroup %>%
  #REVIEW: later, move quartiles to make_data?
  mutate(
    extr_quartiles = case_when(
      extr_prctl <= .25 ~ 1,
      (extr_prctl > .25) & (extr_prctl < .5) ~ 2,
      (extr_prctl > .5) & (extr_prctl <= .75) ~ 3,
      (extr_prctl > .75) ~ 4
    ),
    extr_quartiles = factor(
      extr_quartiles,
      levels = 1:4,
      labels = c(
        "strongly\nintroverted\n(1st quartile)",
        "moderately\nintroverted\n(2nd quartile)",
        "moderately\nextraverted\n(3rd quartile)",
        "strongly\nextraverted\n(4th quartile)"
      )
    )
  ) %>%
  left_join(select(tbl_participants_1, id, starts_with("education")))

```

```{r exp1_AUC}
dat_exp1_AUC <- tbl_targeting_1 %>%
  group_by(id) %>%
  nest %>%
  mutate(
    AUC_CI = map(
      data,
      roc_auc,
      truth = stimuli_is_targeted_fct,
      y = conf_full_range,
      options = list(smooth = FALSE)
    )
  ) %>%
  unnest(AUC_CI)
tbl_targeting_performance_1 <- tbl_targeting_performance_1 %>%
  left_join(select(dat_exp1_AUC, id, AUC = .estimate), by = "id")

```


## Multi-level logistic regression model

```{r mdl_exp1, message=TRUE}
# model was preregistered here: http://aspredicted.org/blind.php?x=wu6sk7 (section 5)
mdl_exp1 <- brm(
  dec_correct ~ 1 + condition + (1 | id) + (1 + condition | stimuli),
  data = tbl_targeting_1,
  family = bernoulli(),
  save_pars = save_pars(group = FALSE),
  file = here("output/study1/models/mdl_exp1"),
  save_model = here("output/study1/models/mdl_exp1.stan"),
  chains = 4,
  iter = iter,
  warmup = warmup,
  thin = thin,
  control = list(adapt_delta = .99),
  seed = 1999
)
mdl_exp1

# Check coding
pull(mdl_exp1$data, condition) %>% levels
fnc_check_coding(pull(mdl_exp1$data, condition))

# Check that the data used in the model is the same as the loaded data
# (in case the model was not rerun because the model file already exists).
expect_equivalent(as_tibble(mdl_exp1$data),
                 select(tbl_targeting_1,  all.vars(as.formula(mdl_exp1$formula))))

```

```{r mdl_exp1_txt}
# export model summary as .txt
summary(mdl_exp1, robust = TRUE) %>%
  utils::capture.output(file = here("output/study1/models/mdl_exp1_summary.txt"))

```






## Difference in percentage points between conditions

```{r mdl_exp1_percentage_points}
mdl_exp1_percentage_points <-
  posterior_samples(mdl_exp1, pars = c("^b_.")) %>%
  as_tibble %>%
  mutate(
    prob_control = inv_logit_scaled(b_Intercept - .5 * b_condition1),
    prob_boosting = inv_logit_scaled(b_Intercept + .5 * b_condition1),
    prob_diff = prob_boosting - prob_control
  ) %>%
  pivot_longer(everything()) %>%
  group_by(name) %>%
  summarise(median_qi(value)) %>%
  filter(str_detect(name, "^prob_")) %>% 
  kable(digits = 2)
mdl_exp1_percentage_points

write_lines(
  mdl_exp1_percentage_points,
  here("output/study1/models/mdl_exp1_percentage_points.md")
)

```



## Effect size

```{r mdl_exp1_effect_sizes}
mdl_exp1_effect_sizes <- posterior_samples(mdl_exp1,
                                           pars = c("b_condition1",
                                                    "sd_id__Intercept")) %>%
  as_tibble %>%
  rename(lo_delta = b_condition1, lo_sd = sd_id__Intercept) %>%
  transmute(CL = pnorm(lo_delta / sqrt(lo_sd ^ 2 + lo_sd ^ 2))) %>%
  pivot_longer(everything()) %>%
  group_by(name) %>%
  summarise(median_qi(value)) %>%
  kable(digits = 2)
mdl_exp1_effect_sizes

write_lines(mdl_exp1_effect_sizes,
            here("output/study1/models/mdl_exp1_effect_sizes.md"))

```




## Figure 2 (main figure for Experiment 1)

```{r fig_exp1_main}
mdl_exp1_ce_condition <-
  conditional_effects(mdl_exp1, re_formula = NA)$condition %>%
  left_join(df_exp1_conditions)

fig_exp1_main <- mdl_exp1_ce_condition %>%
  rename(boosting_str = condition_str) %>%
  ggplot(aes(
    x = fct_rev(boosting_str),
    y = estimate__,
    ymin = lower__,
    ymax = upper__
  )) +
  scale_y_continuous(breaks = pretty_breaks(10)) +
  coord_fixed(ratio = 2, ylim = c(0, 1.025)) +
  geom_pointrange(position = position_nudge(x = .15)) +
  labs(x = "",
       y = acc_str) +
  theme_minimal_hgrid() +
  guides(color = "none")

dat_exp1_props <-
  left_join(tbl_targeting_performance_1, df_exp1_conditions) %>%
  rename(boosting_str = condition_str) %>%
  group_by(boosting_str, acc) %>%
  summarize(n = n()) %>%
  group_by(boosting_str) %>%
  mutate(prop = n / sum(n),
         prop_rounded = fnc_perc(prop)) %>%
  ungroup

fig_exp1_main <- fig_exp1_main +
  geom_point(
    aes(
      x = fct_rev(boosting_str),
      y = acc,
      size = 100 * prop
    ),
    alpha = .15,
    shape = 20,
    position = position_nudge(x = -.15),
    inherit.aes = FALSE,
    data = dat_exp1_props
  ) +
  geom_text(
    aes(
      x = fct_rev(boosting_str),
      y = acc,
      label = prop_rounded
    ),
    alpha = .5,
    size = 2.25,
    position = position_nudge(x = -.15),
    inherit.aes = FALSE,
    data = dat_exp1_props
  ) +
  geom_boxplot(
    aes(condition_str, y = acc),
    width = .05,
    outlier.alpha = 0,
    inherit.aes = FALSE,
    data = left_join(tbl_targeting_performance_1, df_exp1_conditions)
  ) +
  scale_size_area("%", max_size = 10) +
  guides(size = "none") +
  theme(legend.position = "right",
        legend.text = element_text(size = 10))
fig_exp1_main
#TODO: ensure that numbers round up to 100; use the function from the survey repo

save_plot(
  here("output/study1/figures/fig_exp1_main.pdf"),
  fig_exp1_main,
  base_width = 3.5,
  base_height = 3.5
)

```



## SI figures

### Accuracy (ECDF)

```{r fig_exp1_ecdf}
fig_exp1_ecdf <- tbl_targeting_performance_1 %>%
  left_join(df_exp1_conditions) %>%
  rename(boosting_str = condition_str) %>% 
  ggplot(aes(x = acc, color = fct_rev(boosting_str))) +
  coord_fixed() +
  scale_color_brewer("Condition", type = "qual", palette = 2) +
  geom_vline(xintercept = .5, linetype = "dotted") +
  stat_ecdf(size = 1) +
  theme(legend.position = c(0.075, 0.875)) +
  labs(x = acc_str,
       y = "ECDF") +
  guides(color = guide_legend("", reverse = TRUE))

```



### Moderation by extraversion

#### Accuracy vs. continous extraversion percentile

```{r fig_exp1_extr_prctl}
fig_exp1_extr_prctl <- tbl_targeting_performance_1 %>%
  left_join(df_exp1_conditions) %>%
  rename(boosting_str = condition_str) %>% 
  ggplot(aes(
    x = extr_prctl,
    y = acc,
    color = fct_rev(boosting_str),
    fill = fct_rev(boosting_str)
  )) +
  coord_fixed(ratio = 1, ylim = c(0, 1)) +
  scale_x_continuous("Extraversion percentile", breaks = pretty_breaks(10)) +
  scale_y_continuous(acc_str, breaks = pretty_breaks(10)) +
  scale_color_brewer("", type = "qual", palette = 2) +
  scale_fill_brewer("", type = "qual", palette = 2) +
  geom_vline(xintercept = 0.5, linetype = "dotted") +
  geom_hline(yintercept = 0.5, linetype = "dotted") +
  stat_smooth(
    method = "loess",
    method.args = list(family = "symmetric"),
    alpha = .15
  ) +
  # `family = "symmetric"`: re-descending M estimator is used with Tukey's biweight function
  geom_point(alpha = .5, position = position_jitter(height = .01)) +
  theme(
    legend.position = c(.025, .3),
    axis.text = element_text(size = 9)) +
  guides(color = guide_legend(reverse = TRUE),
         fill = guide_legend(reverse = TRUE))

```


#### Accuracy vs. personality percentile quartiles

```{r fig_exp1_extr_quartiles}
dat_exp1_props_extr_quartiles <- tbl_targeting_performance_1 %>%
  left_join(df_exp1_conditions) %>%
  rename(boosting_str = condition_str) %>%
  group_by(boosting_str, extr_quartiles, acc) %>%
  summarize(n = n()) %>%
  group_by(boosting_str, extr_quartiles) %>%
  mutate(prop = n / sum(n),
         prop_rounded = round(100 * prop, 0)) %>%
  ungroup
#COMEBAK `fnc_perc` throws an error


fig_exp1_extr_quartiles_base <- dat_exp1_props_extr_quartiles %>%
  ggplot(
    aes(
      x = extr_quartiles,
      y = acc,
      color = fct_rev(boosting_str),
      group = fct_rev(str_c(boosting_str, extr_quartiles)),
      size = prop,
      label = prop_rounded
    )
  ) +
  coord_fixed(ratio = 2.5, ylim = c(0, 1.025)) +
  theme_minimal_hgrid() +
  labs(x = "") +
  scale_y_continuous(acc_str, breaks = pretty_breaks(10)) +
  scale_color_brewer("", type = "qual", palette = 2) +
  scale_size_area("%", max_size = 9) +
  geom_point(position = position_dodge(width = 1)) +
  geom_text(color = "white",
            size = 2.5,
            position = position_dodge(width = 1)) +
  guides(color = guide_legend(reverse = FALSE),
         size = "none") +
  theme(
    legend.position = "top",
    legend.justification = "center",
    axis.text.x = element_text(size = 9)
  )

fig_exp1_extr_quartiles <- fig_exp1_extr_quartiles_base +
  geom_boxplot(
    aes(size = NULL,
        label = NULL),
    width = .15,
    position = position_dodge(width = .2),
    outlier.alpha = 0,
    data = {
      left_join(tbl_targeting_performance_1, df_exp1_conditions) %>%
        rename(boosting_str = condition_str)
    }
  )

```



#### SI extraversion figure

```{r fig_exp1_SI_extr, fig.width=9, fig.height=4.5}
fig_exp1_SI_extr <- plot_grid(
  fig_exp1_extr_prctl,
  fig_exp1_extr_quartiles,
  nrow = 1,
  axis = "lrtb",
  align = "hv",
  rel_widths = c(.75, 1),
  scale = c(.9, .95),
  hjust = -2,
  vjust = +2.5,
  labels = c("A", "B")
)
fig_exp1_SI_extr

save_plot(
  here("output/study1/figures/fig_exp1_SI_extr.pdf"),
  fig_exp1_SI_extr,
  base_width = 9,
  base_height = 4.5
)

```



### Incorporating confidence judgments (AUC analysis)

#### Confidence-AUC vs. continous extraversion percentile

```{r fig_exp1_auc_extr_prctl}
fig_exp1_auc_extr_prctl <- fig_exp1_extr_prctl +
  aes(y = AUC) +
  scale_y_continuous("AUC")

```


#### Confidence-AUC vs. personality percentile quartiles

```{r fig_exp1_auc_extr_quartiles}
fig_exp1_auc_extr_quartiles <- tbl_targeting_performance_1 %>%
  left_join(df_exp1_conditions) %>%
  rename(boosting_str = condition_str) %>% 
  ggplot(aes(extr_quartiles, AUC, color = fct_rev(boosting_str))) +
  scale_y_continuous(breaks = pretty_breaks(10)) +
  scale_color_brewer("", type = "qual", palette = 2) +
  labs(x = "") +
  geom_boxplot(width = .2, outlier.alpha = 0) +
  geom_point(alpha = .2, position = position_jitterdodge(jitter.width = .15)) +
  theme(legend.position = "top",
        legend.justification = "center")

```


#### SI confidence-AUC figure

```{r fig_exp1_SI_AUC, fig.width=9, fig.height=4.5}
fig_exp1_SI_AUC <- plot_grid(
  fig_exp1_auc_extr_prctl,
  fig_exp1_auc_extr_quartiles,
  nrow = 1,
  axis = "lrtb",
  align = "hv",
  rel_widths = c(.75, 1),
  scale = c(.9, .95),
  hjust = -2,
  vjust = +2.5,
  labels = c("A", "B")
)
fig_exp1_SI_AUC

save_plot(
  here("output/study1/figures/fig_exp1_SI_AUC.pdf"),
  fig_exp1_SI_AUC,
  base_width = 9,
  base_height = 4.5
)

```



### Moderation by education

#### Accuracy vs. education

```{r fig_exp1_education_acc}
dat_exp1_education_n <- tbl_targeting_performance_1 %>%
  filter(!is.na(education_coarse)) %>%
  left_join(df_exp1_conditions) %>%
  rename(boosting_str = condition_str) %>%
  group_by(boosting_str, education_coarse) %>%
  summarize(n = n()) %>%
  mutate(n_str = glue("n = {n}"))

dat_exp1_props_education <- tbl_targeting_performance_1 %>%
  filter(!is.na(education_coarse)) %>%
  left_join(df_exp1_conditions) %>%
  rename(boosting_str = condition_str) %>%
  group_by(boosting_str, education_coarse, acc) %>%
  summarize(n = n()) %>%
  group_by(boosting_str, education_coarse) %>%
  mutate(prop = n / sum(n),
         prop_rounded = round(100 * prop, 0)) %>%
  ungroup
#COMEBAK `fnc_perc` throws an error

fig_exp1_education_acc <- fig_exp1_extr_quartiles_base %+%
  dat_exp1_props_education +
  aes(x = education_coarse,
      group = fct_rev(str_c(education_coarse, boosting_str))) +
  coord_fixed(ratio = 3, ylim = c(-0.0125, 1.025)) +
  geom_boxplot(
    aes(size = NULL,
        label = NULL),
    width = .15,
    position = position_dodge(width = .25),
    outlier.alpha = 0,
    data = {
      left_join(tbl_targeting_performance_1, df_exp1_conditions) %>%
        rename(boosting_str = condition_str) %>%
        filter(!is.na(education_coarse))
    }
  ) +
  geom_text(
    aes(
      x = education_coarse,
      y = -.035,
      group = fct_rev(str_c(education_coarse, boosting_str)),
      label = n_str
    ),
    size = 3,
    position = position_dodge(width = 1),
    data = dat_exp1_education_n,
    inherit.aes = FALSE,
  ) +
  scale_x_discrete(
    "Education level",
    labels = function(x)
      str_wrap(x, width = 10)
  ) +
  theme(axis.text.x = element_text(size = 9))

```


#### Confidence-AUC vs. education

```{r fig_exp1_education_auc}
fig_exp1_education_auc <- fig_exp1_auc_extr_quartiles %+%
  {fig_exp1_auc_extr_quartiles$data %>% 
      left_join(dat_exp1_education_n) %>%
      filter(!is.na(education_coarse))} +
  aes(x = education_coarse) +
  coord_fixed(ratio = 3.125, ylim = c(0, 1.025)) +
  scale_x_discrete("Education level", labels = function(x) str_wrap(x, width = 10)) +
  theme(axis.text.x = element_text(size = 9))

```


#### SI education figure

```{r fig_exp1_education, fig.width=10, fig.height=4.75}
fig_exp1_education <- plot_grid(
  fig_exp1_education_acc,
  fig_exp1_education_auc,
  nrow = 1,
  scale = .95,
  axis = "tblr",
  align = "hv",
  hjust = -2,
  vjust = +2.5,
  labels = c("A", "B")
)
fig_exp1_education

save_plot(
  here("output/study1/figures/fig_exp1_SI_education.pdf"),
  fig_exp1_education,
  base_width = 10,
  base_height = 4.75
)

```


# Experiment 2

## Load data

```{r load_data_experiment2}
tbl_participants_2 <- read_rds(here("output/study2/tbl_participants.rds"))
tbl_targeting_2 <- read_rds(here("output/study2/tbl_targeting.rds"))

```


## Augment data

```{r tbl_targeting_performance_2}
tbl_targeting_performance_2 <- tbl_targeting_2 %>%
  group_by_at(
    vars(
      id,
      questionnaire,
      relevance,
      contains("extr"),
      contains("ATI")
    )
  ) %>%
  summarize(acc = mean(dec_correct),
            conf_in_correct = mean(conf_in_correct)) %>%
  ungroup %>% 
  #REVIEW: later, move quartiles to make_data?
  mutate(
    extr_quartiles = case_when(
      extr_prctl <= .25 ~ 1,
      (extr_prctl > .25) & (extr_prctl < .5) ~ 2,
      (extr_prctl > .5) & (extr_prctl <= .75) ~ 3,
      (extr_prctl > .75) ~ 4
    ),
    extr_quartiles = factor(
      extr_quartiles,
      levels = 1:4,
      labels = c(
        "strongly\nintroverted\n(1st quartile)",
        "moderately\nintroverted\n(2nd quartile)",
        "moderately\nextraverted\n(3rd quartile)",
        "strongly\nextraverted\n(4th quartile)"
      )
    )
  ) %>% 
  left_join(select(tbl_participants_2, id, starts_with("education")))

```

```{r exp2_AUC}
dat_exp2_AUC <- tbl_targeting_2 %>%
  group_by(id) %>%
  nest %>%
  mutate(
    AUC_CI = map(
      data,
      roc_auc,
      truth = stimuli_is_targeted_fct,
      y = conf_full_range,
      options = list(smooth = FALSE)
    )
  ) %>%
  unnest(AUC_CI)
tbl_targeting_performance_2 <- tbl_targeting_performance_2 %>%
  left_join(select(dat_exp2_AUC, id, AUC = .estimate), by = "id")

```




## Multi-level logistic regression model

```{r mdl_exp2, message=TRUE}
# model was preregistered here: http://aspredicted.org/blind.php?x=39ik6v (section 5)
mdl_exp2 <- update(
  mdl_exp1,
  formula. = dec_correct ~ 1 + relevance * questionnaire + (1 | id) + (1 + relevance * questionnaire | stimuli),
  newdata = tbl_targeting_2,
  file = here("output/study2/models/mdl_exp2"),
  save_model = here("output/study2/models/mdl_exp2.stan")
  )
# define the model based on how it differs from `mdl_exp1`
mdl_exp2

# Check coding
pull(mdl_exp2$data, relevance) %>% levels
fnc_check_coding(pull(mdl_exp2$data, relevance))

pull(mdl_exp2$data, questionnaire) %>% levels
fnc_check_coding(pull(mdl_exp2$data, questionnaire))

# Check that the data used in the model is the same as the loaded data
# (in case the model was not rerun because the model file already exists).
expect_equivalent(as_tibble(mdl_exp2$data),
                 select(tbl_targeting_2,  all.vars(as.formula(mdl_exp2$formula))))

```


```{r mdl_exp2_text}
# export model summary as .txt
options(width = 120)
summary(mdl_exp2, robust = TRUE) %>%
  utils::capture.output(file = here("output/study2/models/mdl_exp2_summary.txt"))

```





## Difference in percentage points between conditions

```{r mdl_exp2_percentage_points}
mdl_exp2_percentage_points <-
  posterior_samples(mdl_exp2, pars = c("^b_.")) %>%
  as_tibble %>%
  mutate(
    prob_boosting_quest = inv_logit_scaled(
      b_Intercept + .5 * b_relevance1 + .5 * b_questionnaire1 + .25 * `b_relevance1:questionnaire1`
    ),
    prob_boosting_no_quest = inv_logit_scaled(
      b_Intercept + .5 * b_relevance1 - .5 * b_questionnaire1 - .25 * `b_relevance1:questionnaire1`
    ),
    prob_control_quest = inv_logit_scaled(
      b_Intercept - .5 * b_relevance1 + .5 * b_questionnaire1 - .25 * `b_relevance1:questionnaire1`
    ),
    prob_control_no_quest = inv_logit_scaled(
      b_Intercept - .5 * b_relevance1 - .5 * b_questionnaire1 + .25 * `b_relevance1:questionnaire1`
    ),
    prob_diff_boosting_quest = prob_boosting_quest - prob_boosting_no_quest,
    prob_diff_boosting_control_no_quest = prob_boosting_no_quest - prob_control_no_quest,
    prob_diff_boosting_control_quest = prob_boosting_quest - prob_control_quest
  ) %>%
  pivot_longer(everything()) %>%
  group_by(name) %>%
  summarise(median_qi(value)) %>%
  filter(str_detect(name, "^prob_")) %>% 
  kable(digits = 2)
mdl_exp2_percentage_points

write_lines(
  mdl_exp2_percentage_points,
  here("output/study2/models/mdl_exp2_percentage_points.md")
)

```



## Effect size

```{r mdl_exp2_effect_sizes}
mdl_exp2_effect_sizes <-
  posterior_samples(mdl_exp2, pars = c("^b_.", "^sd_id")) %>%
  as_tibble %>%
  transmute(
    CL_diff_boosting_quest_no_quest = pnorm(((
      b_Intercept + .5 * b_relevance1 + .5 * b_questionnaire1 + .25 * `b_relevance1:questionnaire1`
    ) -
      (
        b_Intercept + .5 * b_relevance1 - .5 * b_questionnaire1 - .25 * `b_relevance1:questionnaire1`
      )
    ) /
      sqrt(sd_id__Intercept ^ 2 + sd_id__Intercept ^ 2)),
    
    CL_diff_boosting_control_no_quest = pnorm(((
      b_Intercept + .5 * b_relevance1 - .5 * b_questionnaire1 - .25 * `b_relevance1:questionnaire1`
    ) -
      (
        b_Intercept - .5 * b_relevance1 - .5 * b_questionnaire1 + .25 * `b_relevance1:questionnaire1`
      )
    ) /
      sqrt(sd_id__Intercept ^ 2 + sd_id__Intercept ^ 2))
    
    ,
    CL_diff_boosting_control_quest = pnorm(((
      b_Intercept + .5 * b_relevance1 + .5 * b_questionnaire1 + .25 * `b_relevance1:questionnaire1`
    ) -
      (
        b_Intercept - .5 * b_relevance1 + .5 * b_questionnaire1 - .25 * `b_relevance1:questionnaire1`
      )
    ) /
      sqrt(sd_id__Intercept ^ 2 + sd_id__Intercept ^ 2))
    
  ) %>%
  pivot_longer(everything()) %>%
  group_by(name) %>%
  summarise(median_qi(value)) %>%
  kable(digits = 2)
mdl_exp2_effect_sizes

write_lines(mdl_exp2_effect_sizes,
            here("output/study2/models/mdl_exp2_effect_sizes.md"))

```



## Figure 3 (main figure for Experiment 2)

```{r fig_exp2_main}
mdl_exp2_ce <-
  conditional_effects(mdl_exp2,
                      effects = "relevance:questionnaire",
                      re_formula = NA)$"relevance:questionnaire" %>%
  left_join(df_exp2_conditions, by = c("relevance", "questionnaire"))

fig_exp2_main <- mdl_exp2_ce %>%
  ggplot(
    aes(
      x = boosting_str,
      color = questionnaire_str,
      y = estimate__,
      ymin = lower__,
      ymax = upper__
    )
  ) +
  coord_fixed(ratio = 1.25, ylim = c(0, 1.025)) +
  scale_y_continuous(breaks = pretty_breaks(10)) +
  scale_color_brewer("Questionnaire", type = "qual", palette = 2) +
  geom_pointrange(position = position_dodge(.25)) +
  labs(x = "",
       y = acc_str) +
  theme_minimal_hgrid() +
  theme(legend.position = c(0.15, 1 - 0.925))

dat_exp2_props <-
  left_join(tbl_targeting_performance_2, df_exp2_conditions) %>%
  group_by(questionnaire_str, boosting_str, acc) %>%
  summarize(n = n()) %>%
  group_by(questionnaire_str, boosting_str) %>%
  mutate(prop = n / sum(n),
         prop_rounded = fnc_perc(prop)) %>%
  ungroup

fig_exp2_main <- fig_exp2_main +
  geom_point(
    aes(
      x = boosting_str,
      color = questionnaire_str,
      y = acc,
      size = 100 * prop
    ),
    alpha = .15,
    shape = 20,
    inherit.aes = FALSE,
    position = position_dodge(1.25),
    data = dat_exp2_props
  ) +
  geom_text(
    aes(
      x = boosting_str,
      color = questionnaire_str,
      y = acc,
      label = prop_rounded
    ),
    alpha = .5,
    size = 2.25,
    position = position_dodge(1.25),
    inherit.aes = FALSE,
    data = dat_exp2_props
  ) +
  geom_boxplot(
    aes(boosting_str, y = acc, color = questionnaire_str),
    width = .075,
    position = position_dodge(.75),
    outlier.alpha = 0,
    inherit.aes = FALSE,
    data = left_join(tbl_targeting_performance_2, df_exp2_conditions)
  ) +
  scale_size_area(max_size = 10) +
  guides(size = "none") +
  theme(
    legend.position = "top",
    legend.justification = "center") +
  guides(color = guide_legend(
    title.position = "left",
    title.hjust = .5,
    reverse = FALSE,
    direction = "horizontal"
  ))
#TODO: ensure that numbers round up to 100; use the function from the survey repo

fig_exp2_main

save_plot(
  here("output/study2/figures/fig_exp2_main.pdf"),
  fig_exp2_main,
  base_width = 5,
  base_height = 3.5
)

```



## SI figures

### Accuracy (ECDF)

```{r fig_exp2_ecdf}
fig_exp2_ecdf <- tbl_targeting_performance_2 %>%
  left_join(df_exp2_conditions) %>% 
  ggplot(aes(x = acc, color = boosting_str, linetype = fct_rev(questionnaire_str))) +
  coord_fixed() +
  scale_color_brewer("", type = "qual", palette = 2) +
  scale_linetype("") +
  geom_vline(xintercept = .5, linetype = "dotted") +
  stat_ecdf(size = 1) +
  theme(legend.position = "top") +
  labs(x = acc_str,
       y = "ECDF")

```


### Moderation by extraversion

#### Accuracy vs. continous extraversion percentile

```{r fig_exp2_extr_prctl}
fig_exp2_extr_prctl <- fig_exp1_extr_prctl %+% {
  left_join(tbl_targeting_performance_2, df_exp2_conditions) %>%
    mutate(questionnaire_str = str_c(questionnaire_str, " questionnaire"))
} +
  aes(color = boosting_str, fill = boosting_str) +
  facet_wrap( ~ fct_rev(questionnaire_str)) +
  theme(legend.position = c(.025, .25))

```



#### Accuracy vs. personality percentile quartiles

```{r fig_exp2_extr_quartiles}
dat_exp2_props_extr_quartiles <- tbl_targeting_performance_2 %>%
  left_join(df_exp2_conditions) %>%
  group_by(boosting_str, questionnaire_str, extr_quartiles, acc) %>%
  summarize(n = n()) %>%
  group_by(boosting_str, questionnaire_str, extr_quartiles) %>%
  mutate(prop = n / sum(n),
         prop_rounded = round(100 * prop, 0)) %>%
  ungroup
#COMEBAK `fnc_perc` throws an error

fig_exp2_extr_quartiles_base <- fig_exp1_extr_quartiles_base %+%
  left_join(dat_exp2_props_extr_quartiles, df_exp2_conditions) +
  facet_wrap( ~ questionnaire_str,
              labeller = labeller(
                questionnaire_str = function(x)
                  glue("{x} questionnaire")
              )) +
  guides(color = guide_legend(reverse = TRUE)) +
  scale_color_brewer("",
                     type = "qual",
                     palette = 2,
                     direction = -1)

fig_exp2_extr_quartiles <- fig_exp2_extr_quartiles_base +
  geom_boxplot(
    aes(size = NULL,
        label = NULL),
    width = .15,
    position = position_dodge(width = .2),
    outlier.alpha = 0,
    data = left_join(tbl_targeting_performance_2, df_exp2_conditions)
  )
fig_exp2_extr_quartiles

```





#### SI extraversion figure

```{r fig_exp2_SI_extr, fig.width=9, fig.height=8.25}
fig_exp2_SI_extr <- plot_grid(
  fig_exp2_extr_prctl,
  fig_exp2_extr_quartiles,
  ncol = 1,
  axis = "lrtb",
  align = "hv",
  rel_heights = c(.75, 1),
  scale = c(1.2, .9),
  hjust = -2,
  vjust = +2.5,
  labels = c("A", "B")
)
fig_exp2_SI_extr

save_plot(
  here("output/study2/figures/fig_exp2_SI_extr.pdf"),
  fig_exp2_SI_extr,
  base_width = 9,
  base_height = 8.25
)

```



### Incorporating confidence judgments (AUC analysis)

#### Confidence-AUC vs. continous extraversion percentile

```{r fig_exp2_auc_extr_prctl}
fig_exp2_auc_extr_prctl <- fig_exp2_extr_prctl +
  aes(y = AUC) +
  scale_y_continuous("AUC")
fig_exp2_auc_extr_prctl

```


#### Confidence-AUC vs. personality percentile quartiles

```{r fig_exp2_auc_extr_quartiles}
fig_exp2_auc_extr_quartiles <- tbl_targeting_performance_2 %>%
  left_join(df_exp2_conditions) %>%
  ggplot(aes(extr_quartiles, AUC, color = boosting_str)) +
  scale_y_continuous(breaks = pretty_breaks(10)) +
  scale_color_brewer("", type = "qual", palette = 2) +
  labs(x = "") +
  geom_boxplot(width = .2, outlier.alpha = 0) +
  geom_point(alpha = .2, position = position_jitterdodge(jitter.width = .15)) +
  facet_wrap( ~ questionnaire_str,
              labeller = labeller(
                questionnaire_str = function(x)
                  glue("{x} questionnaire")
              )) +
  theme(
    legend.position = "top",
    legend.justification = "center",
    axis.text.x = element_text(size = 8)
  )
fig_exp2_auc_extr_quartiles

```


#### SI confidence-AUC figure

```{r fig_exp2_SI_AUC, fig.width=9, fig.height=8.25}
fig_exp2_SI_AUC <- plot_grid(
  fig_exp2_auc_extr_prctl,
  fig_exp2_auc_extr_quartiles,
  ncol = 1,
  axis = "lrtb",
  align = "hv",
  rel_heights = c(.75, 1),
  scale = c(1.2, .9),
  hjust = -2,
  vjust = +2.5,
  labels = c("A", "B")
)
fig_exp2_SI_AUC

save_plot(
  here("output/study2/figures/fig_exp2_SI_AUC.pdf"),
  fig_exp2_SI_AUC,
  base_width = 9,
  base_height = 8.25
)

```


### Moderation by education

#### Accuracy vs. education

```{r fig_exp2_education_acc}
dat_exp2_education_n <- tbl_targeting_performance_2 %>%
  filter(!is.na(education_coarse)) %>%
  left_join(df_exp2_conditions) %>%
  group_by(boosting_str, questionnaire_str, education_coarse) %>%
  summarize(n = n()) %>%
  mutate(n_str = glue("n = {n}"))

dat_exp2_props_education <- tbl_targeting_performance_2 %>%
  filter(!is.na(education_coarse)) %>%
  left_join(df_exp2_conditions) %>%
  left_join(dat_exp2_education_n) %>%
  group_by(boosting_str, questionnaire_str, education_coarse, acc) %>%
  summarize(n = n()) %>%
  group_by(boosting_str, education_coarse) %>%
  mutate(prop = n / sum(n),
         prop_rounded = round(100 * prop, 0)) %>%
  ungroup
#COMEBAK `fnc_perc` throws an error

fig_exp2_education_acc <- fig_exp2_extr_quartiles_base %+%
  dat_exp2_props_education +
  aes(x = education_coarse,
      group = fct_rev(str_c(education_coarse, boosting_str))) +
  coord_fixed(ratio = 3, ylim = c(-0.0125, 1.025)) +
  guides(color = guide_legend(reverse = TRUE)) +
  geom_boxplot(
    aes(size = NULL,
        label = NULL),
    width = .15,
    position = position_dodge(width = .25),
    outlier.alpha = 0,
    data = {
      left_join(tbl_targeting_performance_2, df_exp2_conditions) %>%
        left_join(dat_exp2_education_n) %>%
        filter(!is.na(education_coarse))
    }
  ) +
  geom_text(
    aes(
      x = education_coarse,
      y = -.035,
      group = fct_rev(str_c(education_coarse, boosting_str)),
      label = n_str
    ),
    size = 2.5,
    position = position_dodge(width = 1),
    data =
      dat_exp2_education_n
    ,
    inherit.aes = FALSE,
  ) +
  scale_x_discrete(
    "Education level",
    labels = function(x)
      str_wrap(x, width = 10)
  ) +
  facet_wrap( ~ questionnaire_str,
              labeller = labeller(
                questionnaire_str = function(x)
                  glue("{x} questionnaire")
              )) +
  theme(axis.text.x = element_text(size = 9))
fig_exp2_education_acc

```


#### Confidence-AUC vs. education

```{r fig_exp2_education_auc}
fig_exp2_education_auc <- fig_exp2_auc_extr_quartiles %+%
  {
    fig_exp2_auc_extr_quartiles$data %>%
      left_join(dat_exp2_education_n) %>%
      filter(!is.na(education_coarse))
  } +
  aes(x = education_coarse) +
  coord_fixed(ratio = 3, ylim = c(-0.0125, 1.025)) +
  geom_text(
    aes(
      x = education_coarse,
      y = -.035,
      group = fct_rev(str_c(education_coarse, boosting_str)),
      label = n_str
    ),
    size = 2.5,
    position = position_dodge(width = 1),
    data = dat_exp2_education_n,
    inherit.aes = FALSE,
  ) +
  facet_wrap(~ questionnaire_str,
             labeller = labeller(
               questionnaire_str = function(x)
                 glue("{x} questionnaire")
             )) +
  scale_x_discrete(
    "Education level",
    labels = function(x)
      str_wrap(x, width = 10)
  ) +
  theme(
    axis.text.x = element_text(size = 9),
    strip.text = element_text(face = "plain"))
fig_exp2_education_auc

```



#### SI education figure

```{r fig_exp2_education, fig.width=9, fig.height=9}
fig_exp2_education <- plot_grid(
  fig_exp2_education_acc,
  fig_exp2_education_auc,
  nrow = 2,
  scale = .95,
  axis = "tblr",
  align = "hv",
  hjust = -2,
  vjust = +2.5,
  labels = c("A", "B")
)
fig_exp2_education

save_plot(
  here("output/study2/figures/fig_exp2_SI_education.pdf"),
  fig_exp2_education,
  base_width = 9,
  base_height = 10
)

```

