---
title: "Prepare data Study 1"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Setup

```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  message = TRUE,
  warning = TRUE,
  cache = FALSE,
  autodep = TRUE
  )

```


Source `dependencies.R`.

```{r dependencies, message=FALSE, cache=FALSE, code=readr::read_lines(here::here("code/_dependencies.R"))}
source(here::here("code/_dependencies.R"))

```



# Load data

```{r load_data}
condition <- read_rds(here("data/study1/condition.rds"))
extr <- read_rds(here("data/study1/extr.rds"))
ATI <- read_rds(here("data/study1/ATI.rds"))
detection <- read_rds(here("data/study1/detection.rds"))
check <- read_rds(here("data/study1/check.rds"))
checkopen <- read_rds(here("data/study1/checkopen.rds"))

```



# Participant data frame


## Age

```{r tbl_age}
tbl_age <- inner_join({
  extr %>%
    filter(item_name == "age") %>%
    select(id, age_extr = answer)
},
{
  ATI %>%
    filter(item_name == "age") %>%
    select(id, age_ATI = answer)
}, by = "id") %>%
  type_convert %>%
  assert(within_bounds(18, 99), age_ATI, age_extr) %>%
  assert(not_na, everything())

```


## Education

```{r tbl_education}
tbl_education <- checkopen %>%
  filter(item_name == "eduaction") %>% # "eduaction": typo in data file
  select(id, education_num = answer) %>%
  type_convert %>%
  left_join(df_education_infos, by = "education_num") %>%
  select(-education_num) %>% 
  assert(not_na, everything(), error_fun = warn_report)
# education was a required response

```


```{r education}
tbl_education %>%
  group_by(education) %>%
  summarize(n = n()) %>%
  kable()

```

```{r education_coarse}
tbl_education %>%
  group_by(education_coarse) %>%
  summarize(n = n()) %>%
  kable()

```




## Create treatment variable

```{r tbl_treatment}
tbl_treatment <- condition %>%
  select(id, condition = group) %>%
  mutate(condition = factor(condition - 1,
                            c(1, 0),
                            c("inoculation", "control"))) %>%
  assert(not_na, everything())

# Use deviation coding
contrasts(tbl_treatment$condition) <- "contr.dev"

```




## Personality measures


### Extraversion vs. introversion

```{r tbl_extr}
tbl_extr <- extr %>%
  select(id, item_name, answer) %>%
  filter(str_detect(item_name, "^bfi")) %>%
  type_convert %>%
  assert(not_na, everything()) %>%
  mutate(answer_aligned = ifelse(str_detect(item_name, "R"),
                                 5 + 1 - answer, answer)) %>%
  group_by(id) %>%
  summarize(extr = mean(answer_aligned)) %>%
  assert(not_na, everything()) %>%
  inner_join(select(tbl_age, id, age = age_extr), by = "id") %>%
  assert(not_na, everything()) %>%
  mutate(extr_norm = map2(extr, age,
                          fnc_find_extr_prctl)) %>%
  unnest(extr_norm) %>%
  select(-age) %>%
  assert(not_na, everything())
tbl_extr

# Use deviation coding
contrasts(tbl_extr$extr_type) <- "contr.dev"

```


### ATI

```{r tbl_ATI}
# Norms are from
# 
# Franke, T., Attig, C., & Wessel, D. (2019). A personal resource for technology interaction: development and validation of the affinity for technology interaction (ATI) scale. International Journal of Human–Computer Interaction, 35(6), 456-467. https://doi.org/10.1080/10447318.2018.1456150
# 
# Sample "S5-full", Table 1 (p. 459)

tbl_ATI <- ATI %>%
  select(id, item_name, answer) %>%
  filter(str_detect(item_name, "^ATI")) %>%
  type_convert %>%
  assert(not_na, everything()) %>%
  mutate(answer_aligned = ifelse(str_detect(item_name, "R"),
                                 5 + 1 - answer, answer)) %>%
  group_by(id) %>%
  summarize(ATI = mean(answer_aligned)) %>%
  assert(not_na, everything()) %>%
  semi_join(tbl_age, by = "id") %>%
  mutate(
    ATI_prctl = pnorm(q = ATI, mean = 3.09, sd = 0.86),
    ATI_type = case_when(ATI_prctl > .5 ~ "affine",
                         ATI_prctl <= .5 ~ "non-affine",
                         TRUE ~ "NA"),
    ATI_pro = abs(ATI_prctl - .5)
  )
tbl_ATI

```




## Combine data

```{r tbl_participants}
tbl_participants <- tbl_age %>%
  select(id, age = age_ATI) %>%
  left_join(tbl_education, by = "id") %>%
  inner_join(select(tbl_treatment, id, condition), by = "id") %>%
  left_join(tbl_extr, by = "id") %>%
  left_join(tbl_ATI, by = "id")
tbl_participants

```



# Targeting task

```{r tbl_targeting}
tbl_targeting <- detection %>%
  semi_join(tbl_participants, by = "id") %>%
  select(id, item_name, answer) %>%
  filter(str_detect(item_name, "^mc_target|^confidence")) %>%
  assert(not_na, everything()) %>%
  mutate(
    stimuli = str_extract(item_name, "\\d{1,2}"),
    response = ifelse(str_detect(item_name, "^mc_target"), "dec", "conf")
  ) %>%
  pivot_wider(
    id_cols = c("id", "stimuli"),
    names_from = "response",
    values_from = "answer"
  ) %>%
  assert(not_na, everything()) %>%
  type_convert %>%
  # dec: 1 = "yes
  mutate(dec = ifelse(dec == 2, 0, 1),
         dec_fct = factor(dec, c(1, 0))) %>%
  assert(in_set(1:5), conf) %>%
  assert(in_set(0:1), dec) %>%
  assert(not_na, everything()) %>%
  left_join(tbl_stimuli, by = "stimuli") %>%
  left_join(
    select(
      tbl_participants,
      id,
      condition,
      contains("extr"),
      contains("ATI", ignore.case = FALSE)
    ),
    by = "id"
  ) %>%
  assert(not_na, everything()) %>%
  mutate(
    stimuli_is_targeted = case_when(
      stimuli_target == extr_type ~ TRUE,
      stimuli_target != extr_type ~ FALSE,
      TRUE ~ NA
    ),
    stimuli_is_targeted_fct = factor(stimuli_is_targeted * 1, c(1, 0)),
    dec_correct = (stimuli_is_targeted == dec) * 1,
    conf_full_range = ifelse(dec == 1, conf, -conf),
    conf_in_correct = ifelse(dec == 1, conf, 5 + 1 - conf)
  )
tbl_targeting

## check:
# tbl_targeting %>%
#   select(stimuli_target, extr_type, stimuli_is_targeted) %>%
#   table

```


# Data exclusion criteria

We preregistered the following data exclusion criteria (see <http://aspredicted.org/blind.php?x=wu6sk7>):

> 6) Describe exactly how outliers will be defined and handled, and your precise rule(s) for excluding observations.
> 
> We will exclude participants that:
> 
> 1. have already participated in the pilot study.
> 2. did not complete the survey.
> 3. have a relative extraversion percentile of 50%. For these participants no extraversion personality type can be assigned.
> 4. provided different answers for the two questions asking them to indicate their age in the first and second personality questionnaire.
> 5. fail an instruction check for the targeting detection task thrice. After the instructions, but before starting the targeting detection task, participants are shown a multiple-choice question probing whether they correctly understood the targeting detection task (1 correct vs. 3 incorrect response options). If a participant selects an incorrect option, the question is displayed again up to two times; the response options are sorted differently each time. After three incorrect responses, the participants can continue the study, but will be excluded from all analyses.


## 1) have already participated in the pilot study

These participants were screened out by Prolific Academic's platform, so no need to do it here.


## 2) did not complete the survey

```{r exclude_incomplete}
# list of uncompleted IDs (participants who entered the survey but did not reach the last question)

# the following two participants did not finish the study (i.e., missing education)
# BdxzjCTTqlVxianwtx9yZn3jv1hQM8VMFaYoS6zr_ATOkwp8vKGBi8_M0DsPcvWh
# uGB0sH1XFYbx7pTIxk8kGd2CrbqnQPfXHwp3w-2NcCADtw6bmPhaonMsPipRPx_G

tbl_exclude_incomplete <- anti_join(select(condition, id),
                                    {
                                      checkopen %>%
                                        filter(item_name == "page1") %>%
                                        select(id)
                                    }, by = "id") %>%
  bind_rows(
    tibble(id = c(
      "BdxzjCTTqlVxianwtx9yZn3jv1hQM8VMFaYoS6zr_ATOkwp8vKGBi8_M0DsPcvWh",
      "uGB0sH1XFYbx7pTIxk8kGd2CrbqnQPfXHwp3w-2NcCADtw6bmPhaonMsPipRPx_G"
    ))
  ) %>% 
  mutate(exclude_incomplete = TRUE)

```


## 3) have a relative extraversion percentile of 50%. For these participants no extraversion personality type can be assigned

```{r exclude_extr_prctl_50}
tbl_exclude_extr_prctl_50 <- tbl_participants %>%
  filter(extr_prctl == .5) %>% 
  select(id) %>% 
  mutate(exclude_extr_prctl_50 = TRUE)

```


## 4) provided different answers for the two questions asking them to indicate their age in the first and second personality questionnaire

```{r exclude_age_diff}
tbl_exclude_age_diff <- tbl_age %>%
  filter(age_ATI != age_extr) %>%
  select(id) %>%
  mutate(exclude_age_diff = TRUE)

```


## 5) fail an instruction check for the targeting detection task thrice

```{r exclude_instruction_check}
tbl_answer_key <- tribble(
  ~item_name,                       ~correct,
   "multiplechoice_comprehension1",  2,
   "multiplechoice_comprehension2",  4,
   "multiplechoice_comprehension3",  1,
)

tbl_multiplechoice_comprehension <- check %>%
  select(id, item_name, answer, displaycount) %>%
  filter(str_detect(item_name, "^multiple")) %>%
  left_join(tbl_answer_key, by = "item_name") %>%
  mutate(correct = answer == correct) %>%
  filter(not_na(answer)) %>%
  group_by(id) %>%
  summarize(failed_n = sum(correct == FALSE))

tbl_multiplechoice_comprehension %>%
  pull(failed_n) %>%
  table %>%
  kable

tbl_exclude_instruction_check <-
  tbl_multiplechoice_comprehension %>%
  filter(failed_n == 3) %>%
  select(id) %>%
  mutate(exclude_instruction_check = TRUE)

```


## Combine exclusion criteria

```{r tbl_exclude}
tbl_exclude <- list(
  tbl_exclude_incomplete,
  tbl_exclude_extr_prctl_50,
  tbl_exclude_age_diff,
  tbl_exclude_instruction_check
) %>%
  reduce(full_join, by = "id")

# get treatment of exclusions
exclude_treatment <- inner_join(tbl_treatment, tbl_exclude, by = "id")

n_exclude <- tbl_exclude %>%
  pull(id) %>%
  n_distinct

```

`r n_exclude` participants will be excluded.


## Exclude `r n_exclude` participants

```{r exclude}
tbl_participants <- tbl_participants %>%
  anti_join(tbl_exclude, by = "id") %>%
  assert(not_na, everything())
tbl_participants

tbl_targeting <- tbl_targeting %>%
  anti_join(tbl_exclude, by = "id") %>% 
  assert(not_na, everything())
tbl_targeting


# exclude_treatment %>%
#   group_by_at(setdiff(names(exclude_treatment), "id")) %>%
#   count(name = "n")

tbl_exclusion_summary <- data.frame(
  condition = c("boosting", "control"),
  consented_n = c(nrow(filter(condition, group == 2)), nrow(filter(condition, group == 1))),
  not_completed = c(nrow(
    filter(
      exclude_treatment,
      exclude_incomplete == TRUE &
        condition == "inoculation"
    )
  ), nrow(
    filter(
      exclude_treatment,
      exclude_incomplete == TRUE & condition == "control"
    )
  )),
  fiftieth_percentile = c(nrow(
    filter(
      exclude_treatment,
      exclude_extr_prctl_50 == TRUE &
        condition == "inoculation"
    )
  ), nrow(
    filter(
      exclude_treatment,
      exclude_extr_prctl_50 == TRUE & condition == "control"
    )
  )),
  age_mismatch = c(nrow(
    filter(
      exclude_treatment,
      exclude_age_diff == TRUE &
        condition == "inoculation"
    )
  ), nrow(
    filter(
      exclude_treatment,
      exclude_age_diff == TRUE & condition == "control"
    )
  )),
  failed_compr_check = c(nrow(
    filter(
      exclude_treatment,
      exclude_instruction_check == TRUE &
        condition == "inoculation"
    )
  ), nrow(
    filter(
      exclude_treatment,
      exclude_instruction_check == TRUE & condition == "control"
    )
  )),
  final_n = c(nrow(
    filter(tbl_participants, condition == "inoculation")
  ), nrow(
    filter(tbl_participants, condition == "control")
  ))
) %>%
  mutate(prop_retained = round(final_n / consented_n, 2))

kable(tbl_exclusion_summary)

```



# Check overlap id's in both data frames

Participants need to appear in both data frames.

```{r check_id_overlap}
expect_equal(nrow(anti_join(tbl_participants, tbl_targeting)), 0)
expect_equal(nrow(anti_join(tbl_targeting, tbl_participants)), 0)

```



# Save data to disk

```{r save_data}
write_rds(tbl_participants,
          here("output/study1/tbl_participants.rds"),
          compress = "gz")
write_csv(tbl_participants,
          here("output/study1/tbl_participants.csv"))

write_rds(tbl_targeting,
          here("output/study1/tbl_targeting.rds"),
          compress = "gz")
write_csv(tbl_targeting, here("output/study1/tbl_targeting.csv"))

```
